Summary: Dissertation Proposal

### 2021-01-16 r/Paper_analyses.Rmd
clearing out old files

## GAMM results (see 5.8.19)

@@

# summary + plots from best models
summary(gamm10$gam)
plot(gamm10$gam,pages=1)
```

Predicting grazing intensity (site-level means, island as random effect)
```{r, echo=F, message=F, warning=F}
m_data <- sum_ssp_pca

@@

gtab_fi_site <- as.data.frame(rbind(g1,g2,g3,g5,g6,g7,g8,g9,g10,g11,g12)) %>% setNames(c("g","Model", "AICc", "Adj. R2")) %>% arrange(AICc)
kable(gtab_fr_site)

@@

summary(gamm12$gam)
```

>>>>

## GAMM results

@@

# summary + plots from best models
plot(gamm12$gam,pages=1)

summary(gamm12$gam)
summary(gamm10$gam)
summary(gamm2$gam)
```

Predicting grazing intensity (site-level means, island as random effect)
```{r, echo=F, message=F, warning=F}
m_data <- sum_ssp_pca
remove(g1, g2, g4, g6, g7, g8, g9, g10, g11, g12)

@@

gtab_fi_site <- as.data.frame(rbind(g1,g2,g3,g5,g6,g7,g8,g9,g10,g11,g12)) %>% setNames(c("g","Model", "AICc", "Adj. R2")) %>% arrange(AICc)
kable(gtab_fi_site)

@@

summary(gamm12$gam)
summary(gamm10$gam)
summary(gamm2$gam)
```

### 2021-01-16 r/old_code/Ch2 outline_V3.Rmd
clearing out old files

site <- read.csv(here("data", "site.csv"), strip.white = T, stringsAsFactors = F) %>% select(-X)
sum_id <- read.csv(here("data","sum_id.csv"), stringsAsFactors=F) %>%
  select(-X) %>% 
  filter(phase == "i" & 
           species_code %in% c("stop","qup") & 
           length_cm <= 30 & length_cm >= 15 & 
           !(species_code == "stop" & site == "Pallaster West") & 
           !(species_code == "qup" & site %in% c("Pallaster East","Rendezvous","Turtle Bay"))) %>%
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island) %>%
  filter(fr <= 3000)

sum_ssp_sub <- sum_id %>% 
  group_by(species, species_code, site, island) %>%
  summarize(
    n=n(),
    length_median=median(length_cm),
    length_se=sd(length_cm)/sqrt(n),
    g_frac_median=median(g_frac),
    g_frac_median=median(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_median=median(br,na.rm=TRUE),
    br_median=median(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_median=median(fr),
    fr_median=median(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_median=median(for_dur,na.rm=TRUE),
    for_dur_median=median(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_median=median(for_bites,na.rm=TRUE),
    for_bites_median=median(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n)
    ) %>%
  left_join(site, by = c("island","site"))

@@

```{r, eval = F, echo = F, message=F, warning=F}
# grazing impact (vg ~ volume grazed) of fish from behavioral surveys
sum_id_vg <- sum_id %>%
  filter(species_code != "rbp") %>%
  mutate(
    bs = ifelse(species_code == "stop", 5.257*10^-4*length_cm^2, 4.013*10^-4*length_cm^2), # adding bite size equations from Mumby
    bh_capped = ifelse(ta_canopy < 2*sqrt(bs)/(22/7), ta_canopy, 2*sqrt(bs)/(22/7)), # if ta_canopy exceeds diameter of bite size, bite height is capped at bite size
    bv = bs*ta_canopy,
    bv_capped = bs*bh_capped,
    vg = fr*bv,
    vg_capped = fr*bv_capped,
    island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))
) %>%
  arrange(island)

## PCA
```{r, echo=F, message=F, warning=F}
pca_pred <- prcomp(na.omit(site %>%
                remove_rownames %>% column_to_rownames(var="site") %>%
                select(rugosity, ma_cover, ma_canopy, ta_cover, ta_canopy, scar_den, scar_bm, carn30_bm, lc_cover)),
  center = T, scale = T)

autoplot(pca_pred, data = site, shape = 'island', colour = 'island',
         label = T,
         loadings = T, loadings.colour = 'gray',
         loadings.label = T, loadings.label.size = 3, loadings.label.colour = 'black',
            loadings.label.repel = T) +
    scale_color_manual(values = c("cadetblue3","cadetblue3","cadetblue3")) +
    theme_bw() +
    theme(legend.title = element_blank())
ggsave(here("figs/pca_pred.png"), width = 8, height = 5)

sum_id_pca <- sum_id %>% 
  left_join(select(sum_site,site,pc1_all,pc2_all), by = "site")
sum_ssp_pca <- sum_ssp_sub %>%
  left_join(select(sum_site,site,pc1_all,pc2_all), by = "site")
```

### Better PCA?
```{r, echo=F, message=F, warning=F}
pca_data <- na.omit(site %>%
  select(rugosity, ma_cover, ma_canopy, ta_cover, ta_canopy, lc_cover, scar_bm, scar_den, carn30_bm))
names(pca_data)[1:9] =
  c("rugosity", "macroalgal cover", "macroalgal canopy", "turf cover", "turf canopy", "coral cover", "scarid biomass", "scarid density", "predator biomass")

@@

fviz_pca_biplot(pca_pred,
                col.ind = site$island,
                mean.point = F,
                label = "var",
                repel = T
                ) +
  scale_shape_manual(values=c(15,16,17)) +
  scale_color_manual(values = c("black","black","black")) +
  labs(x = "PC1 (55.6%)", y = "PC2 (24.5%)", title = "") +
  theme_bw() +
  theme(legend.title = element_blank())

ggsave(here("figs/pca_pred.png"), width = 7, height = 5)

@@

@@

gtab_fr_site <- as.data.frame(rbind(g1,g2,g4,g5,g6,g7,g8,g9,g10,g11,g12)) %>% setNames(c("g","Model", "AICc", "Adj. R2")) %>% arrange(AICc)

# summary + plots from best models
summary(gamm12$gam)
plot(gamm12$gam,pages=1)
```

@@

gtab_fi_site <- as.data.frame(rbind(g1,g2,g3,g4,g5,g6,g7,g8,g9,g10,g11,g12)) %>% setNames(c("g","Model", "AICc", "Adj. R2")) %>% arrange(AICc)

@@

# Supplement

@@

### loess plots for additional drivers?

>>>>

sum_site <- read.csv(here("data", "site.csv"), strip.white = T, stringsAsFactors = F) %>% select(-X)
sum_id <- read.csv(here("data","sum_id.csv"), stringsAsFactors=F) %>%
  select(-X) %>% 
  filter(phase == "i" & 
           species_code %in% c("stop","qup") &
           length_cm <= 30 & length_cm >= 15 &
           ### excluding sites with less than 7 observations within size subset range
           !(species_code == "stop" & site == "Pallaster West") & 
           !(species_code == "qup" & site %in% c("Pallaster East","Rendezvous","Turtle Bay"))) %>%
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island) %>%
  filter(fr <= 3000)

sum_ssp_sub <- sum_id %>% # size subset 15-30cm
  group_by(species, species_code, site, island) %>%
  summarize(
    n=n(),
    length_mean=mean(length_cm),
    length_median=median(length_cm),
    length_se=sd(length_cm)/sqrt(n),
    g_frac_median=median(g_frac),
    g_frac_median=median(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_median=median(br,na.rm=TRUE),
    br_median=median(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_median=median(fr),
    fr_median=median(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_median=median(for_dur,na.rm=TRUE),
    for_dur_median=median(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_median=median(for_bites,na.rm=TRUE),
    for_bites_median=median(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n)
    ) %>%
  left_join(sum_site, by = c("island","site"))

@@

## PCA

```{r, eval=F, echo=F, message=F, warning=F}
### old code for other plot version
# pca_pred <- prcomp(na.omit(sum_site %>%
#                 remove_rownames %>% column_to_rownames(var="site") %>%
#                 select(rugosity, ma_cover, ma_canopy, ta_cover, ta_canopy, scar_den, scar_bm, carn30_bm, lc_cover)),
#   center = T, scale = T)
# 
# autoplot(pca_pred, data = sum_site, shape = 'island', colour = 'island',
#          label = F,
#          loadings = T, loadings.colour = 'gray',
#          loadings.label = T, loadings.label.size = 3, loadings.label.colour = 'black',
#             loadings.label.repel = T) +
#     scale_color_manual(values = c("cadetblue3","cadetblue3","cadetblue3")) +
#     theme_bw() +
#     theme(legend.title = element_blank())
# ggsave(here("figs/pca_pred.png"), width = 8, height = 5)
```
```{r, echo=F, message=F, warning=F}
pca_data <- na.omit(sum_site %>%
  select(rugosity, ma_cover, ma_canopy, ta_cover, ta_canopy, lc_cover, scar_bm, scar_den, carn30_bm))
names(pca_data)[1:9] =
  c("rugosity", "macroalgal cover", "macroalgal canopy", "turf cover", "turf canopy", "coral cover", "scarid biomass", "scarid density", "predator biomass")

@@

fviz_pca_biplot(pca_pred,
                col.ind = sum_site$island,
                mean.point = F,
                label = "var",
                repel = T
                ) +
  scale_shape_manual(values=c(15,16,17)) +
  scale_color_manual(values = c("black","black","black")) +
  labs(x = "PC1 (55.6%)", y = "PC2 (24.5%)", title = "") +
  theme_bw() +
  theme(legend.title = element_blank())

ggsave(here("figs/pca_pred.png"), width = 7, height = 5)
```

```{r}
sum_site_pca <- sum_site %>% 
  bind_cols(as.data.frame(pca_pred$x) %>% 
           select(PC1,PC2)) %>%
  rename(pc1_all=PC1,
         pc2_all=PC2)

sum_id_pca <- sum_id %>% 
  left_join(select(sum_site_pca,site,pc1_all,pc2_all), by = "site")
sum_ssp_pca <- sum_ssp_sub %>%
  left_join(select(sum_site_pca,site,pc1_all,pc2_all), by = "site")
```

@@

Note that these GAMMs are using the size subsetted data, as opposed to the full size ranges

@@

gtab_fr_site <- as.data.frame(rbind(g1,g2,g3,g4,g5,g6,g7,g8,g9,g10,g11,g12)) %>% setNames(c("g","Model", "AICc", "Adj. R2")) %>% arrange(AICc)
kable(gtab_fr_site)

# summary + plots from best models
summary(gamm10$gam)
plot(gamm10$gam,pages=1)
```

@@

gtab_fi_site <- as.data.frame(rbind(g1,g2,g3,g5,g6,g7,g8,g9,g10,g11,g12)) %>% setNames(c("g","Model", "AICc", "Adj. R2")) %>% arrange(AICc)

@@

# Supplement/optional

@@

### Loess plots for additional drivers?

### Grazing impact evaluation
```{r, eval = F, echo = F, message=F, warning=F}
# grazing impact (vg ~ volume grazed) of fish from behavioral surveys
sum_id_vg <- sum_id %>%
  filter(species_code != "rbp") %>%
  mutate(
    bs = ifelse(species_code == "stop", 5.257*10^-4*length_cm^2, 4.013*10^-4*length_cm^2), # adding bite size equations from Mumby
    bh_capped = ifelse(ta_canopy < 2*sqrt(bs)/(22/7), ta_canopy, 2*sqrt(bs)/(22/7)), # if ta_canopy exceeds diameter of bite size, bite height is capped at bite size
    bv = bs*ta_canopy,
    bv_capped = bs*bh_capped,
    vg = fr*bv,
    vg_capped = fr*bv_capped,
    island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))
) %>%
  arrange(island)

### 2021-01-16 r/old_code/Data_prodding.Rmd
clearing out old files

Notes 11/11:
* figure out dcast issues
* replacing NA/0s within pipe

```{r,message=FALSE,warning=FALSE, echo=FALSE}
# set up
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
library(startR)
library(here)
library(tidyverse)
library(corrplot)
library(ggplot2)
library(RColorBrewer)
library(ggfortify)
library(ggsignif) # boxplot stats
library(EnvStats) # boxplot stats
library(car)
library(nlme)
# library(gamm4)
# library(xtable)
```
```{r,message=FALSE,warning=FALSE, echo=FALSE}
sum_site <- read.csv(here("data","sum_site.csv"), stringsAsFactors=F) %>%
  select(-X) %>%
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island)
sum_id <- read.csv(here("data","sum_id.csv"), stringsAsFactors=F) %>%
  select(-X) %>%
  filter(length_cm>=15)
sum_ssp <- read.csv(here("data","sum_ssp.csv"), stringsAsFactors=F) %>%
  select(-X) 
fish <- read.csv(here("data","fish.csv"), stringsAsFactors=F) %>%
  select(-X) 
```

@@

```{r}
sample <- group_by(sum_id, site, species, species_code, phase, island) %>% summarize(n=n())

ggplot(sample, aes(x=factor(site, levels = sum_site$site), y=n)) +
        facet_grid(phase~species) +
        geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
        scale_fill_manual(values = c("gray", "slategray2", "black")) +
        labs(title="Total sample") +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
```{r}
ggplot(filter(sample, species_code!="rbp" & phase == "i"),
      aes(x=factor(site, levels = sum_site$site), y=n)) +
        facet_grid(.~species) +
        geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
        scale_fill_manual(values = c("gray", "slategray2", "black")) +
        labs(title="Sample subset") +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

>>>>

```{r,message=FALSE,warning=FALSE, echo=FALSE}
# set up
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
library(startR)
library(here)
library(tidyverse)
library(corrplot)
library(ggplot2)
library(RColorBrewer)
library(ggfortify)
library(ggsignif) # boxplot stats
library(EnvStats) # boxplot stats
library(car)
library(nlme)
# library(gamm4)
# library(xtable)
```

```{r,message=FALSE,warning=FALSE, echo=FALSE}
sum_site <- read.csv(here("data","sum_site.csv"), stringsAsFactors=F) %>%
  select(-X) %>%
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island)
sum_id <- read.csv(here("data","sum_id.csv"), stringsAsFactors=F) %>%
  select(-X) %>%
  filter(length_cm>=15)
sum_ssp <- read.csv(here("data","sum_ssp.csv"), stringsAsFactors=F) %>%
  select(-X) 
fish <- read.csv(here("data","fish.csv"), stringsAsFactors=F) %>%
  select(-X) 
```

@@

```{r}
sample_tot <- sum_id %>%
  filter(species_code != "rbp" & phase == "i") %>%
  group_by(site, species, species_code, phase, island) %>% 
  summarize(n=n())
sample_28 <- sum_id %>%
  filter(species_code != "rbp" & phase == "i" & length_cm <= 28) %>%
  group_by(site, species, species_code, phase, island) %>% 
  summarize(n=n())
sample_30 <- sum_id %>%
  filter(species_code != "rbp" & phase == "i" & length_cm <= 30) %>%
  group_by(site, species, species_code, phase, island) %>% 
  summarize(n=n())

ggplot(sample_tot, aes(x=factor(site, levels = sum_site$site), y=n)) +
        facet_grid(phase~species) +
        geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
        scale_fill_manual(values = c("gray", "slategray2", "black")) +
        labs(title="Total sample") +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
```{r}
ggplot(filter(sample, species_code!="rbp" & phase == "i"),
      aes(x=factor(site, levels = sum_site$site), y=n)) +
        facet_grid(.~species) +
        geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
        scale_fill_manual(values = c("gray", "slategray2", "black")) +
        labs(title="Sample subset") +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### 2021-01-16 r/old_code/Grazing_impact.Rmd
clearing out old files

```{r}
# testing size distribution...
sum_id_sub <- sum_id %>%
  filter(length_cm >= 15 & length_cm <= 30 & species_code %in% c("qup", "stop") & phase == "i")

ggplot(data = sum_id_sub, aes(x = site, y = length_cm, group = site)) +
  geom_boxplot() +
  facet_grid(. ~ species)

ggplot(data = sum_id_sub, aes(x = length_cm, group = site, fill = site)) +
  geom_density(alpha = 0.1)

lm <- lm(data = sum_ssp_pca, pc1_all ~ length_mean)
summary(lm) # not significantly correlated with PC1
```

@@

ggplot(filter(ag_melt, island == "Antigua"),
      aes(x=reorder(site, -area_grazed), y=area_grazed)) +
        geom_bar(aes(fill = source), position = "dodge", stat = "identity") +
        scale_fill_manual(values = c("black", "slategray2")) +
        labs(x = "Site", 
             y = expression(Area~grazed~(m^2)~per~Hour), 
            title = expression(Predicted~cumulative~grazing~impact~on~Antiguan~reefs~(m^2/hr))) +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggsave(here("figs/grazing_imp.png"))
```

@@

ggsave(here("figs/bc_point_panel.png"),g)
```

>>>>

@@

ggplot(filter(ag_melt, island == "Antigua"),
      aes(x=reorder(site, -area_grazed), y=area_grazed)) +
        geom_bar(aes(fill = source), position = "dodge", stat = "identity") +
        scale_fill_manual(values = c("black", "slategray2")) +
        labs(x = "Site", 
             y = expression(Area~grazed~(m^2)~per~Hour), 
            title = expression(Predicted~cumulative~grazing~impact~on~Antiguan~reefs~(m^2/hr))) +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1))
#ggsave(here("figs/grazing_imp.png"))
```

@@

#ggsave(here("figs/bc_point_panel.png"),g)
```

### 2021-01-16 r/old_code/Models.Rmd
clearing out old files

*Re: Nash et al. 2016: should I be aggregating data to the site level?*
```{r}
m_data2 <- sum_ssp_pca %>% filter(species_code!="rbp") # currently doesn't work when removing rbp data
gamm2 <- gamm(fr_mean ~ species_code + phase + s(length_m) + s(pc1_bent) + s(pc2_bent) + s(scar_bm), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = sum_ssp_pca
           )
summary(gamm2$gam)
plot(gamm2$gam,pages=1)
plot(gamm2$lme) # not too heteroskedastic?
AIC(gamm2$lme)

# Confirming low VIF among predictor variables with site-level model
lme1 <- lme(fr_mean ~ phase + length_m + scar_bm + pc1_bent + pc2_bent, data=sum_ssp_pca,
    random = ~1 | island, 
    na.action = na.omit
    )
vif(lme1)
```

@@

# Main effects only
gamm1 <- gamm(fr_mean ~ species_code + s(length_m) + phase + s(pc1_all) + s(pc2_all), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
summary(gamm1$gam)
plot(gamm1$gam,pages=1)
plot(gamm1$lme) # not too heteroskedastic?
AIC(gamm1$lme)

# Interactions
gamm2 <- gamm(fr_mean ~ species_code + phase + s(length_m, by = factor(species_code)) + s(pc2_all)  + s(pc1_all, by = factor(species_code)), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
summary(gamm2$gam)
plot(gamm2$gam,pages=1)
plot(gamm2$lme) # not too heteroskedastic?
AIC(gamm2$lme)
# Slightly significant interaction between pc1_all and species_code=qup, but this has lower R2 than model with all main effects
# length/species and pc2/species interactions were not significant

>>>>

*Re: Nash et al. 2016: should I be aggregating data to the site level?*
```{r}
m_data2 <- sum_ssp_pca %>% filter(species_code!="rbp") # currently doesn't work when removing rbp data
gamm2 <- gamm(fr_mean ~ species_code + phase + s(length_mean) + s(pc1_bent) + s(pc2_bent) + s(scar_bm), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = sum_ssp_pca
           )
summary(gamm2$gam)
plot(gamm2$gam,pages=1)
plot(gamm2$lme) # not too heteroskedastic?
AIC(gamm2$lme)

# Confirming low VIF among predictor variables with site-level model
lme1 <- lme(fr_mean ~ phase + length_mean + scar_bm + pc1_bent + pc2_bent, data=sum_ssp_pca,
    random = ~1 | island, 
    na.action = na.omit
    )
vif(lme1)
```

@@

# Main effects only
gamm1 <- gamm(fr_mean ~ species_code + s(length_mean) + phase + s(pc1_all) + s(pc2_all), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
summary(gamm1$gam)
plot(gamm1$gam,pages=1)
plot(gamm1$lme) # not too heteroskedastic?
AIC(gamm1$lme)

# Interactions
gamm2 <- gamm(fr_mean ~ species_code + phase + s(length_mean, by = factor(species_code)) + s(pc2_all)  + s(pc1_all, by = factor(species_code)), 
           family = gaussian(link=identity),
           random = list(island=~1),
           method = "REML",
           data = m_data
           )
summary(gamm2$gam)
plot(gamm2$gam,pages=1)
plot(gamm2$lme) # not too heteroskedastic?
AIC(gamm2$lme)
# Slightly significant interaction between pc1_all and species_code=qup, but this has lower R2 than model with all main effects
# length/species and pc2/species interactions were not significant

### 2021-01-16 r/old_code/SummaryOrals.Rmd
clearing out old files

```{r,message=FALSE,warning=FALSE, echo=FALSE}
# set up
library(rmarkdown)
library(dplyr)
library(tidyr)
library(lazyeval)
library(ggplot2)
library(ellipse)
library(RColorBrewer)
# library(ggbiplot)
library(nlme)
library(pls)
library(mgcv)
library(ggsignif)
library(car)
library(reshape2)
library(EnvStats)
```
```{r,message=FALSE,warning=FALSE, echo=FALSE}
setwd("~/github/Scarid-Behavior/data")
site.sum <- read.csv("site.sum.csv", stringsAsFactors=FALSE) %>% select(-X)
data <- read.csv("data2.csv", stringsAsFactors=FALSE) %>% filter(!(Species.Code=="qup" & Site=="Turtle Bay")) %>% filter(!(Species.Code=="qup" & Site=="Pallaster East")) # remove due to low sample size

vetvir <- data %>% filter(Species.Code!="rbp")
vetvirinit <- vetvir %>% filter(Phase=="i")
vetvir20 <- vetvir %>% filter(Length.cm>=15 & Length.cm<=25)
init20<- vetvir %>% filter(Length.cm>=15 & Length.cm<=25 & Phase=="i")
vetvirAB <- vetvir %>% filter(Island!="Barbuda")
vetvirAB20 <- vetvir %>% filter(Island!="Barbuda")
vetvirABinit <- vetvirAB %>% filter(Phase=="i")

vetvirAB20NS <- vetvirAB20 %>% filter(Site!="Snapper Point")
vetvir20NS <- vetvir20 %>% filter(Site!="Snapper Point")
vetvirNS <- vetvir %>% filter(Site!="Snapper Point")
```

@@

areagrazed.site <- as.data.frame(areagrazed.site)
AG <- melt(areagrazed.site, id=c("Site","Island")) %>% dplyr::rename("data.source"=variable, "area.grazed"=value)
```
```{r}
AG.ANU <- AG %>% filter(Island=="Antigua")
ggplot(data=AG.ANU, aes(x=Site, y=area.grazed, fill=data.source)) +
    geom_bar(stat="identity", position=position_dodge()) + theme_bw() + scale_fill_manual(values=c("black","lightslategrey"),name=expression(paste("Feeding rates \n obtained from:")),breaks=c("personal", "standard"), labels=c("fished data", "unfished data")) + labs(y=expression(Area~Grazed~(m^2/hr)), title=("Predicted site-level grazing impact of Antiguan scarids")) + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("areagrazed.png")
```

>>>>

```{r,message=FALSE,warning=FALSE, echo=FALSE}
# set up
library(here)
library(janitor)
library(tidyr)
library(ggplot2)
library(ellipse)
library(RColorBrewer)
library(nlme)
library(pls)
library(mgcv)
library(ggsignif)
library(car)
library(reshape2)
library(EnvStats)
```
```{r,message=FALSE,warning=FALSE, echo=FALSE}
site.sum <- read.csv(here("data","sum_site.csv"), stringsAsFactors=F) %>% 
  select(-X) %>%
  janitor::clean_names(case="old_janitor")
data <- read.csv(here("data","sum_id.csv"), stringsAsFactors=F) %>%
  filter(!(species_code=="qup" & site=="Turtle Bay")) %>% 
  filter(!(species_code=="qup" & Site=="Pallaster East")) # remove due to low sample size
```

@@

area <- as.data.frame(areagrazed.site)
AG <- melt(areagrazed.site, id=c("Site","Island")) %>% dplyr::rename("data.source"=variable, "area.grazed"=value)
```
```{r}
AG.ANU <- AG %>% filter(Island=="Antigua")
ggplot(data=AG.ANU, aes(x=Site, y=area.grazed, fill=data.source)) +
    geom_bar(stat="identity", position=position_dodge()) + theme_bw() + scale_fill_manual(values=c("black","lightslategrey"),name=expression(paste("Feeding rates \n obtained from:")),breaks=c("personal", "standard"), labels=c("fished data", "unfished data")) + labs(y=expression(Area~Grazed~(m^2/hr)), title=("Predicted site-level grazing impact of Antiguan scarids")) + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("areagrazed.png")
```
